Alex's Notes and Text Fragments for the JOSS Manuscript

### 2021-04-22 paper/paper.Rmd
keywords

  The goal of [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is to gather the available spatiotemporal resampling methods in R and make them available to users through a simplified and generic interface.
  The latter is made possible by integrating the package directly into the [mlr3](https://mlr3.mlr-org.com) machine learning framework.
  This simplifies the step of integrating package specific syntax into an overarching machine learning pipeline.
  The hope is that the availability of such a package encourages researchers to more often apply spatiotemporal resampling methods in scientific case studies.
keywords:
  # at least one keyword must be supplied
  formatted: [resampling, machine learning, autocorrelation, spatial, temporal, "\\proglang{R}"]
  plain:     [resampling, machine learning, autocorrelation, spatial, temporal, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{adjustbox}
  \usepackage{multirow}
  \usepackage{tabularx}
  \usepackage{placeins}
tables: true
bibliography: paper.bib
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
---

>>>>

  The goal of [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is to gather the available spatiotemporal resampling methods in R and make them available to users through a simplified and generic interface.
  The latter is made possible by integrating the package directly into the [mlr3](https://mlr3.mlr-org.com) machine learning framework.
  This simplifies the step of integrating package specific syntax into an overarching machine learning pipeline.
  The hope is that the availability of such a package encourages researchers to more often apply spatiotemporal resampling methods in scientific case studies.
keywords:
  # at least one keyword must be supplied
  formatted: [cross-validation, predictive performance, machine learning, autocorrelation, spatial, temporal, "\\proglang{R}"]
  plain:     [cross-validation, predictive performance, autocorrelation, spatial, temporal, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{adjustbox}
  \usepackage{multirow}
  \usepackage{tabularx}
  \usepackage{placeins}
tables: true
bibliography: paper.bib
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
---
